---
title: "Introduction to StatComp20059"
author: '20059'
date: "2020/12/18"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatComp20059}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__StatComp20059__ is a simple R package developed by 20059 for the Statistical Computing course instructed by Zhang Hong. It includes a softmax function __softmax__ (calculates the softmax value of the input) and a tanh function __tanh__ (calculates the tanh value of the input). 

In addition, the __stock_predict__ function could predict the probability of a stock going up tomorrow, and the stock's name is the argument of this function, e.g. 'AAPL'.

Besides, all my homework answers are included in this package.

## softmax

The __softmax__ function calculates the softmax value of the input, which is one of the typical activation functions in machine learning.

The source R code for __softmax__ is as follows:

```{r 1}
softmax <-function(x) {
  return (exp(x)/sum(exp(x)))
}
```

The softmax function returns the softmax values of the input data, which could be in form of a matrix, a list, a vector...

For example,

```{r 2}
library(StatComp20059)
x=c(15,7,10,23,46,8,33)
sx <- softmax(x)
list(x=x,softmax_x=sx)
```


## tanh

The __tanh__ function calculates the tanh value of the input, which is one of the typical activation functions in machine learning.

The source R code for __tanh__ is as follows:

```{r 3}
tanh <-function(x) {
  return ((exp(x)-exp(-x))/(exp(x)+exp(-x)))
}
```

The tanh function returns the tanh values of the input data, which could be in form of a matrix, a list, a vector...

For example,

```{r 4}
library(StatComp20059)
x <- c(0.15,0.77,-0.10,2.3,-0.46,0.8,-3.3)
tanhx <- tanh(x)
list(x=x,tanh_x=tanhx)
```

## stock_predict
The __stock_predict__ function predicts the probability of a stock going up tomorrow, and the code is as follows:

```{r 5,eval=FALSE}
library(StatComp20059)
stock_predict<-function(symbol)
{

  #To ignore the warnings during usage
  options(warn=-1)
  options("getSymbols.warning4.0"=FALSE)
  #Importing price data for the givensymbol
  data<-data.frame(xts::as.xts(get(quantmod::getSymbols(symbol))))

  #Assighning the column names
  colnames(data) <-c("data.Open","data.High","data.Low","data.Close","data.Volume","data.Adjusted")

  #Creating lag and lead features ofprice column.
  data <-xts::xts(data,order.by=as.Date(rownames(data)))
  data <- as.data.frame(merge(data,lm1=stats::lag(data[,'data.Adjusted'],c(-1,1,3,5,10))))

  #Extracting features from Date
  data$Date<-as.Date(rownames(data))
  data$Day_of_month<-as.integer(format(as.Date(data$Date),"%d"))
  data$Month_of_year<-as.integer(format(as.Date(data$Date),"%m"))
  data$Year<-as.integer(format(as.Date(data$Date),"%y"))
  data$Day_of_week<-as.factor(weekdays(data$Date))

  #Naming variables for reference
  today <- 'data.Adjusted'
  tommorow <- 'data.Adjusted.5'

  #Creating outcome
  data$up_down <-as.factor(ifelse(data[,tommorow] > data[,today], 1, 0))

  #Creating train and test sets
  train<-data[stats::complete.cases(data),]
  test<-data[nrow(data),]

  #Training model
  model<-stats::glm(up_down~data.Open+data.High+data.Low+data.Close+
                      data.Volume+data.Adjusted+data.Adjusted.1+
                      data.Adjusted.2+data.Adjusted.3+data.Adjusted.4+
                      Day_of_month+Month_of_year+Year+Day_of_week,
                    family=binomial(link='logit'),data=train)

  #Making Predictions
  pred<-as.numeric(stats::predict(model,test[,c('data.Open','data.High','data.Low','data.Close','data.Volume','data.Adjusted','data.Adjusted.1','data.Adjusted.2','data.Adjusted.3','data.Adjusted.4','Day_of_month','Month_of_year','Year','Day_of_week')],type= 'response'))

  #Printing results
  print("Probability of Stockprice going up tommorow:")
  print(pred)
}

stock_predict('GOOGL')
```
